### 2019-07-10 2-Chapters/Conclusion/conclusion.tex
BOUM

In order to validate our results in a realistic experimental setting and not only with simulations, future works should include a hardware implementation of the analyzed models, in order to complete our demonstration presented in Section~\ref{sec:4:gnuradio} \cite{Besson2018ICT,Besson2019WCNC}.
%
A hardware demonstrator could be also benefit to study other settings by relaxing some hypotheses, for instance by studying a similar model in non-slotted time.

@@

\begin{center}
    Merci d'avoir lu cette thèse.
    Thanks for reading this document.
\end{center}

@@

% \vfill{}

>>>>

% In order to validate our results in a realistic experimental setting and not only with simulations, future works should include a hardware implementation of the analyzed models, in order to complete our demonstration presented in Section~\ref{sec:4:gnuradio} \cite{Besson2018ICT,Besson2019WCNC}.
% %
% A hardware demonstrator could be also benefit to study other settings by relaxing some hypotheses, for instance by studying a similar model in non-slotted time.

@@

\begin{center}
    Je vous remercie d'avoir lu cette thèse. Merci de me signaler toute erreur par courriel :
    \\
    Thanks for reading this document. Please notify me about any mistake by e-mail:\\
    \href{https://github.com/Naereen/phd-thesis/issues/new}{\texttt{Lilian.Besson}\texttt{@}\texttt{Crans.org}}
\end{center}

@@
